---
title: "linear model from Web"
author: "Sisilia Martinez"
date: "Summer 2022"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

## Model 1 SIM~ARMS

### scatterplot

```{r}
plot(SIMS~ARM,data=data)
```

Looking at the scatter plot you can infer that as the ARM increases, SIMS increase as well.

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

Looking at the numerical results the independent variable is ARM and the dependent variable is SIMS. Which makes this a positive correlation because the number given in the numerical result was positive. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

When we fit the equation of the line that fits the data is SIMS = -4.095(the intercept) + .0545 * ARM.

#### Predict at target point

```{r}
tgp=data.frame(ARM=88, GRIP=94)
predict.lm(model.1, tgp, interval = "prediction")
```

The prediction for when ARMS is equal 88 is 0.7063836.

#### scatterplot with model fit
  
```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
basicNN + geom_point() + geom_lm()
```

## Model 2 SIM~GRIP

```{r}
basicNN_GRIP <- ggplot(data,aes(y=SIMS,x=GRIP))
```

### Now add in scatterplot

```{r}
basicNN_GRIP + geom_point()
```

This scatter plot shows a positive correlation between SIMS and GRIP.

### Numerical results 

```{r}
cor(SIMS~GRIP,data=data)
```

This allows us to see that there is a positive correlation between SIMS and GRIP. However the correlation between SIMS and ARM had a higher number which shows us that they are more closely correlated than SIMS and GRIP.

### Inferential  (Build model.2)
 
```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
 
The inferential results gave a standard deviation of 1.295 and an adjusted R squared of 0.4053. Which is a higher standard deviation compared to SIMS and ARM.

#### predict model.2 at target point

```{r}
predict.lm(model.2, tgp, interval = "prediction")
```

#### now add the model fit to our plot for model.2
  
```{r}
basicNN_GRIP + geom_point() + geom_lm()
```


## Model 3 SIM~ARM+GRIP

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
The correlation when using ARM and GRIP is higher than just using ARM and GRIP by themselves. 
  
### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

lm(formula = SIMS = -5.433871 + 0.037311 * ARM + 0.024470 * GRIP, data = data)

#### predict model.3 at target point
  

## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2

